Final Report: Scenario 2 - MPX in the EU

### 2022-12-07 Final Report: Scenario 2 - MPX in the EU.Rmd
Combining Final Reports

To prepare this report our team uses data sets for the EU, explicitly including information on confirmed cases of MPX per country (euro_mpx_cases.csv) and census data (euro_census_stats.csv). The trajectory of this investigation incorporated four sets of data manipulation:
(1) Grouping countries into regions;
(2) Assessing necessary census information;
(3) Compiling data sets with confirmed case demographics;
(4) Creating tables and figures for visual analysis.
Countries were grouped by region based on a region's data set (world_country_regions.csv) to enhance the representation of positive cases per region. Within the euro_mpx_cases data set, relevant fields include country, country code, and confirmed cases. A curated demographic data set included information on age, sex, and the number of people per strata. 
As an aside with the census data, we chose to initially assess any "missing" data as "NA" when paired with a country. However then decided to print information with omit-NA's to allow aggregate fields to be added together for "Table 2: Population Demographic (Population Density) per Region."

@@

@@

In Table 1, we see that the regions in EU include various numbers of countries, thus
having unequal populations. A useful metric to create a graph will be
the calculation of cases per 100,000. This will allow us to use one
categorical variable (EU Region) to a quantitative variable (number of
confirmed cases). We compiled the relevant confirmed case information per region in the
EU.

@@

```{r Population Density Demographic Table, echo=FALSE}
kable(Table_2a,
      col.names = c("Population Density", "Eastern Europe", "Northern Europe",
                    "Southern Europe","Western Asia","Western Europe"),
      caption = "Population Demographic (Population Density) per Region") %>%
  kable_styling(latex_options = "HOLD_position")
```

Table 2 illustrates the strata of individuals living within each region of the EU by the population density of that region.

@@

```{r Age Demographic table, echo=FALSE}

@@

Table 3 summarizes the region demographics by age using data that provides information by region based on age in specific brackets.

>>>>

To prepare this report our team uses data sets for the EU, explicitly including information on confirmed cases of MPX per country (euro_mpx_cases.csv) and census data (euro_census_stats.csv). The trajectory of this investigation incorporated four sets of data manipulation:
(1) Grouping countries into regions;
(2) Assessing necessary census information;
(3) Compiling data sets with confirmed case demographics;
(4) Creating tables and figures for visual analysis.

Countries were grouped by region based on a region's data set (world_country_regions.csv) to enhance the representation of positive cases per region. Within the euro_mpx_cases data set, relevant fields include country, country code, and confirmed cases. A curated demographic data set included information on age, sex, and the number of people per strata.   
As an aside with the census data, we chose to initially assess any "missing" data as "NA" when paired with a country. However then decided to print information with omit-NA's to allow aggregate fields to be added together for review of population demographic (Population Density) per Region"

@@

```
\newpage

@@

In Table 1, we see that the regions in EU include various numbers of countries, thus
having unequal populations. A useful metric to create a graph will be
the calculation of cases per 100,000. This will allow us to use one
categorical variable (EU Region) to a quantitative variable (number of
confirmed cases). We compiled the relevant confirmed case information per region in the
EU with the cumulative case rate per 100k represented in the 3rd column.

@@

```{r Population Density Demographic Table, eval=FALSE, include=FALSE}
kable(Table_2a,
      col.names = c("Population Density", "Eastern Europe", "Northern Europe",
                    "Southern Europe","Western Asia","Western Europe"),
      caption = "Population Demographic (Population Density) per Region") %>%
  kable_styling(latex_options = "HOLD_position")
```

@@

```{r Age Demographic table, eval=FALSE, include=FALSE}

@@
